Fusing Filters with Integer Linear Programming

### 2014-06-19 2014betterfusionforfilters/section/06-Related.tex
minor changes
mention rompf

>>>>

Greedy and heuristic approaches that operate on lists of bindings rather than the graph, such as Rompf~\cite{rompf2013optimizing}, can find optimal clusterings in some cases, but are subject to changes in the order of bindings. In these cases, reordering bindings can produce a different clustering, leading to unpredictable runtime performance.
